---
title: "Cross-Platform Data Analytics for a Nigerian Digital Media Company"
author: "Tobi Oyetoro"
date: today
format:
  html:
    theme: flatly
    toc: true
    toc-depth: 3
    toc-title: "Table of Contents"
    code-fold: true
    self-contained: true
    smooth-scroll: true
    highlight-style: github
    fig-width: 10
    fig-height: 6
execute:
  warning: false
  message: false
  echo: true
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(ggcorrplot)
library(scales)
library(patchwork)
library(RColorBrewer)
library(tidytext)
library(tm)
library(wordcloud)
library(textdata)
library(sentimentr)
library(topicmodels)
library(triangle)
library(fitdistrplus)
library(ggridges)
library(prophet)
library(survival)
library(survminer)
library(ggsurvfit)
library(rfm)
library(arules)
library(arulesViz)
library(knitr)
library(kableExtra)
library(DT)
library(plotly)

knitr::opts_chunk$set(
  fig.align  = "center",
  out.width  = "100%",
  dpi        = 150
)

theme_ndmc <- theme_minimal(base_size = 12) +
  theme(
    plot.title    = element_text(face = "bold", size = 14,
                                 colour = "#1F4E79"),
    plot.subtitle = element_text(size = 11, colour = "#595959"),
    plot.caption  = element_text(size = 8,  colour = "#595959"),
    axis.title    = element_text(face = "bold"),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )

file_path <- "/Users/danieloyetoro/Downloads/LBS/YEAR 2/DA/TAKEHOME EXAM/dataybl.xlsx"
```

# 1. Executive Summary

This report presents a cross-platform data analytics study of a
Lagos-based Nigerian entertainment news and lifestyle media company
that publishes media content daily across four platforms
simultaneously: a WordPress website, Facebook, Instagram, and Twitter/X. The organisation, which has been operating since 2013,
generates revenue through Google AdSense, platform-native advertising,
sponsored content partnerships, and direct advertiser relationships.
To protect commercial confidentiality, the organisation is not
identified by name in this report.

Five advanced analytical techniques were applied to real cross-platform
data spanning 2020 to 2026, drawing on 198 text documents across four platforms comprising 
39 website articles selected randomly, 61 Instagram posts and 
50 Facebook posts selected by top reach, and 50 Twitter/X tweets 
selected by top impressions; supplemented by 40 months of revenue 
records, 1,216 days of website traffic, a purposive sample of 107 
advertiser clients drawn from a broader base of approximately 1,826, 
and 500 content path observations from Google Analytics 4.

Sentiment analysis reveals that Facebook generates the most positive
audience reaction at 56% positive sentiment, while Twitter/X is the
most polarising platform with the highest negative sentiment at 28%.
Monte Carlo simulation across 10,000 runs places the organisation's
most likely monthly profit at ₦26.3 million, with a pessimistic floor
of ₦12.6 million and an optimistic ceiling of ₦39.7 million, with Instagram Sponsored Posts identified as the single most volatile
revenue stream. Prophet forecasting reveals a sustained downward trend
in website traffic since 2023, with daily views projected to decline
from a mean of 83,250 to approximately 27,813 by May 2026, driven by
a structural shift in audience consumption toward social platforms.
People analytics exposes a critical commercial vulnerability: 70.1%
of the organisation's 107 advertiser clients have churned, with
survival probability falling below 50% by the 18-month mark.
Association rules confirm that Music and Relationships content
co-occur most strongly in browsing sessions, followed by Celebrity
Gist and Relationships, suggesting a clear content clustering
opportunity.

The overarching recommendation is that the organisation must urgently
implement a social-first content strategy to capture the audience
migrating away from the website, while simultaneously launching a
structured advertiser retention programme targeting the 21 At Risk
clients identified by RFM analysis before they join the 75 already
inactive.

---

# 2. Professional Disclosure

## 2.1 Role and Organisation

I serve as the **Digital Media Manager and Content Strategist** at a
Lagos-based Nigerian digital media and PR company
that has been operating since 2013. The organisation publishes original
content daily across five platforms simultaneously: a self-hosted
WordPress website, Facebook, Instagram, Twitter/X, and WhatsApp. It
generates revenue through Google AdSense, Instagram sponsored content, branded posts, direct
advertiser partnerships, and display advertising. The organisation
has an established audience base predominantly in Nigeria with
significant diaspora reach across the United Kingdom, United States,
Canada, and Ghana. To protect commercial confidentiality, the
organisation is referred to generically throughout this report rather
than by its trading name.

## 2.2 Technique Justifications

**Text Analytics and Sentiment Analysis:** As Digital Media Manager,
understanding how audiences emotionally respond to different content
categories is central to editorial planning. By analysing the sentiment
of post captions and audience comments across platforms, I can identify
which content categories generate positive audience reactions and which
topics require more careful framing. This directly informs daily
publishing decisions.

**Monte Carlo Simulation:** The company's revenue arrives from multiple
uncertain streams, AdSense earnings fluctuate with traffic and dollar
exchange rates, sponsored content income varies month to month, and
platform monetisation is unpredictable. Monte Carlo simulation
quantifies the range of possible monthly profit outcomes and identifies
which revenue stream contributes most to financial uncertainty. This
supports content investment decisions.

**Advanced Forecasting with Prophet:** Forecasting future website
traffic and cross-platform audience reach allows the company to plan
content calendars, negotiate ad inventory in advance, and prepare for
seasonal traffic spikes around events like BBNaija premieres, AFCON
tournaments, and award seasons.

**Customer and People Analytics:** The company's advertiser clients are
its most commercially significant relationships. Analysing client
retention, churn risk, lifetime value, and RFM segments allows them
to identify which clients to prioritise for relationship management and
where to focus business development efforts.

**Association Rules:** Understanding which content categories audiences
consume together in the same browsing session enables the company to
optimise internal linking, plan content scheduling, and sequence social
media posts strategically.

---

# 3. Data Collection and Sampling

## 3.1 Primary Datasets

```{r data-provenance-table}
tibble(
  Dataset = c(
    "Website article performance",
    "Instagram post performance",
    "Facebook post performance",
    "Twitter/X post performance",
    "Revenue and cost records",
    "Cross-platform traffic",
    "Advertiser client records",
    "Content path data"
  ),
  Source = c(
    "Google Analytics 4",
    "Instagram Insights",
    "Meta Business Suite",
    "X Analytics",
    "Internal financial records",
    "GA4 + Platform Insights",
    "Internal campaign records",
    "GA4 Pages and Screens"
  ),
  Period = c(
    "2023–2026",
    "May 2025–Apr 2026",
    "May 2025–Apr 2026",
    "May 2025–Apr 2026",
    "2023–2026",
    "Jan 2023–Apr 2026",
    "2020–2026",
    "Mar–Apr 2026"
  )
) %>%
  kable(caption = "Primary Datasets Used in This Analysis") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE
  )
```

## 3.2 Data Provenance

All datasets were collected directly from platform dashboards operated
by the organisation. Google Analytics 4 data was exported from the
organisation's GA4 property. Social media data was exported from Meta
Business Suite, Instagram Professional Dashboard, and X Analytics.
Financial data was reconstructed from Google AdSense records, payment
receipts, and internal expense logs. Advertiser client data was
compiled from WhatsApp campaign records, direct message histories,
and bank transfer records with client identities anonymised to
CLIENT-001 format.

No personally identifiable information was included in any dataset.
Social media data represents aggregated post-level performance not
individual user records. Advertiser records were anonymised prior to
analysis. The organisation's identity has been withheld from this
published report to protect commercial confidentiality, in accordance
with standard academic research practice. The author confirms that
written consent to use and publish this data in anonymised form was
obtained from the organisation prior to submission.

## 3.3 Sampling Justification

Each dataset was sampled using a method appropriate to its source
and analytical purpose.

Website articles: 39 article URLs were selected randomly from the
organisation's published content archive on Google Analytics 4,
covering the period January 2023 to April 2026. Random selection
was used to avoid cherry-picking high-performing content and to
ensure the sample reflects the typical range of content published
rather than only exceptional performers.

Instagram posts: 61 posts were selected by ranking all available
posts by reach within the export window of January 2025 to April
2026 and retaining the top performers. Reach was chosen as the
selection criterion because it represents the broadest measure of
content exposure on the platform, ensuring the sample captures
posts with sufficient audience signal for meaningful sentiment and
engagement analysis. The export window was constrained to January
2025 to April 2026 due to Instagram Insights data retention
limitations.

Facebook posts: 50 posts were selected by ranking all available
posts by reach within the export window of January 2025 to April
2026 and retaining the top performers. The same rationale applied
as for Instagram; reach provides the most reliable indicator of
content exposure and audience signal. The export window reflects
Meta Business Suite data availability for this property.

Twitter/X posts: 50 tweets were selected by ranking all available
tweets by impressions within the export window of May 2025 to April
2026 and retaining the top performers. Impressions was used as the
selection criterion as it is the primary reach metric on the
platform. The shorter export window reflects X Analytics data
retention constraints for this account.

Revenue and cost records: All available monthly financial records
from January 2023 to April 2026 were used, producing 40 monthly
observations. No sampling was applied, this represents the complete
available financial history for the organisation across that period,
drawn from Google AdSense records, platform monetisation dashboards,
and internal expense logs.

Cross-platform traffic time series: The complete daily traffic
history from Google Analytics 4 was used for the website component,
covering January 2023 to April 2026 and producing 1,216 daily
observations. Social media time series data was constrained to the
available export windows, January 2025 to April 2026 for Facebook
and Instagram, and May 2025 to April 2026 for Twitter/X.. due to
platform data retention limitations. The website daily history
serves as the primary Prophet forecasting variable given its longer
and more complete time range.

Advertiser client records: The organisation's client base numbers
approximately 1,826 advertisers accumulated since 2013. A purposive
sample of 107 clients was constructed using a mixed approach: the
top 10 clients by total historical spend were selected deliberately
to ensure the highest-value relationships were represented in the
analysis, while the remaining 97 were selected randomly from the
broader client population. This approach balances the need to
capture commercially significant clients with the statistical
benefits of random selection for the broader sample. The sample was
drawn from systematically retrievable records including payment
receipts, WhatsApp campaign logs, and direct message histories.
While the 107-client sample does not represent the complete client
population, it captures sufficient behavioural depth across business
categories and campaign histories to support meaningful RFM
segmentation, survival analysis, and CLV modelling.

Association rules data: Pages were selected from the GA4 Pages and
Screens report covering March to April 2026, the maximum available
window for the Explore section of GA4. The top pages by total
sessions were retained after filtering for pages with a minimum of
two sessions to ensure co-consumption signal was present, producing
500 page observations for analysis. The two-month window reflects
GA4 Explore data retention constraints for standard properties
rather than a deliberate sampling decision.

---

# 4. Data Description

```{r load-data}
website   <- read_excel(file_path, sheet = "website")
instagram <- read_excel(file_path, sheet = "instagram")
facebook  <- read_excel(file_path, sheet = "facebook")
x_twitter <- read_excel(file_path, sheet = "x")
revenue   <- read_excel(file_path, sheet = "revenue_cost_montecarlo")
traffic   <- read_excel(file_path, sheet = "traffic_timeseries_prophet")
clients   <- read_excel(file_path, sheet = "people_analytics")
assoc     <- read_excel(file_path, sheet = "association_rules")

cat("Datasets loaded:\n")
cat("Website articles:      ", nrow(website),   "\n")
cat("Instagram posts:       ", nrow(instagram), "\n")
cat("Facebook posts:        ", nrow(facebook),  "\n")
cat("Twitter/X posts:       ", nrow(x_twitter), "\n")
cat("Revenue months:        ", nrow(revenue),   "\n")
cat("Traffic time series:   ", nrow(traffic),   "\n")
cat("Advertiser clients:    ", nrow(clients),   "\n")
cat("Association rules data:", nrow(assoc),     "\n")
```

```{r clean-data}
# ── Website ──────────────────────────────────────────────────
website <- website %>%
  mutate(
    publish_date = as.Date(publish_date),
    article_category = as.factor(article_category),
    views = as.numeric(views),
    active_users = as.numeric(active_users),
    views_per_active_user = as.numeric(views_per_active_user),
    average_engagement_time_per_active_user_sec =
      as.numeric(average_engagement_time_per_active_user_sec),
    event_count = as.numeric(event_count)
  ) %>%
  filter(!is.na(views), views > 0)

# ── Instagram ────────────────────────────────────────────────
instagram <- instagram %>%
  mutate(
    article_category = as.factor(article_category),
    content_type = as.factor(content_type),
    across(c(views, reach, likes, comments,
             shares, saves, engagement_rate_pct), as.numeric)
  ) %>%
  filter(!is.na(reach), reach > 0)

# ── Facebook ─────────────────────────────────────────────────
facebook <- facebook %>%
  mutate(
    date = as.Date(date),
    article_category = as.factor(article_category),
    content_type = as.factor(content_type),
    across(c(views, reach, reactions, comments,
             shares, total_clicks,
             engagement_rate_pct), as.numeric),
    seconds_viewed = as.numeric(seconds_viewed),
    average_seconds_viewed = as.numeric(average_seconds_viewed)
  ) %>%
  filter(!is.na(reach), reach > 0)

# ── Twitter/X ────────────────────────────────────────────────
x_twitter <- x_twitter %>%
  mutate(
    article_category = as.factor(article_category),
    content_type = as.factor(content_type),
    across(c(impressions, likes, engagements,
             bookmarks, shares, replies,
             reposts, engagement_rate_pct), as.numeric)
  ) %>%
  filter(!is.na(impressions), impressions > 0)

# ── Revenue ──────────────────────────────────────────────────
revenue <- revenue %>%
  mutate(
    year = as.integer(year),
    across(where(is.character), ~ na_if(.x, "")),
    across(c(total_revenue_ngn, total_cost_ngn,
             net_profit_ngn, profit_margin_pct,
             ngn_usd_rate), as.numeric)
  ) %>%
  filter(!is.na(total_revenue_ngn))

# ── Traffic ──────────────────────────────────────────────────
traffic <- traffic %>%
  mutate(
    Date = as.Date(Date),
    across(-Date, as.numeric)
  ) %>%
  arrange(Date) %>%
  filter(!is.na(Date), !is.na(website_views))

# ── Clients ──────────────────────────────────────────────────
clients <- clients %>%
  mutate(
    first_campaign_date = as.Date(first_campaign_date),
    last_campaign_date  = as.Date(last_campaign_date),
    churn_date = if_else(
      churn_flag == 1,
      last_campaign_date,
      as.Date(NA)
    ),
    business_category = as.factor(business_category),
    business_size     = as.factor(business_size),
    active_inactive   = as.factor(active_inactive),
    churn_flag        = as.integer(churn_flag),
    total_campaign_runs = as.integer(total_campaign_runs),
    across(c(total_spend_ngn,
             average_spend_per_campaign_ngn,
             days_since_last_campaign), as.numeric)
  ) %>%
  filter(!is.na(first_campaign_date))

# ── Association rules ────────────────────────────────────────
assoc <- assoc %>%
  rename(
    page_path      = Page_path_and_screen_class,
    views_per_sess = views_per_session,
    avg_eng_time   = average_engagement_time_per_session
  ) %>%
  mutate(
    sessions       = as.numeric(sessions),
    views_per_sess = as.numeric(views_per_sess),
    avg_eng_time   = as.numeric(avg_eng_time)
  ) %>%
  filter(!is.na(sessions), sessions >= 2)
# ── Standardise category names across all platforms ──────────
website <- website %>%
  mutate(article_category = str_to_title(str_trim(
    as.character(article_category))))

instagram <- instagram %>%
  mutate(article_category = str_to_title(str_trim(
    as.character(article_category))))

facebook <- facebook %>%
  mutate(article_category = str_to_title(str_trim(
    as.character(article_category))))

x_twitter <- x_twitter %>%
  mutate(article_category = str_to_title(str_trim(
    as.character(article_category))))

cat("All datasets cleaned successfully\n")
```

```{r data-overview}
# ── Content distribution across platforms ─────────────────────
all_content <- bind_rows(
  website   %>%
    select(article_category) %>%
    mutate(platform = "Website"),
  instagram %>%
    select(article_category) %>%
    mutate(platform = "Instagram"),
  facebook  %>%
    select(article_category) %>%
    mutate(platform = "Facebook"),
  x_twitter %>%
    select(article_category) %>%
    mutate(platform = "Twitter/X")
)

all_content %>%
  count(platform, article_category) %>%
  pivot_wider(
    names_from  = platform,
    values_from = n,
    values_fill = 0
  ) %>%
  kable(
    caption = "Content Distribution by Category and Platform"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE
  )

# ── Website numeric summary ───────────────────────────────────
website %>%
  select(views, active_users,
         views_per_active_user,
         average_engagement_time_per_active_user_sec) %>%
  summary() %>%
  kable(caption = "Website Article Performance — Summary Statistics") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )

# ── Engagement rate summary across platforms ──────────────────
bind_rows(
  instagram %>%
    summarise(
      platform = "Instagram",
      avg_engagement_rate = mean(engagement_rate_pct,
                                 na.rm = TRUE),
      median_engagement_rate = median(engagement_rate_pct,
                                      na.rm = TRUE),
      max_engagement_rate = max(engagement_rate_pct,
                                na.rm = TRUE)
    ),
  facebook %>%
    summarise(
      platform = "Facebook",
      avg_engagement_rate = mean(engagement_rate_pct,
                                 na.rm = TRUE),
      median_engagement_rate = median(engagement_rate_pct,
                                      na.rm = TRUE),
      max_engagement_rate = max(engagement_rate_pct,
                                na.rm = TRUE)
    ),
  x_twitter %>%
    summarise(
      platform = "Twitter/X",
      avg_engagement_rate = mean(engagement_rate_pct,
                                 na.rm = TRUE),
      median_engagement_rate = median(engagement_rate_pct,
                                      na.rm = TRUE),
      max_engagement_rate = max(engagement_rate_pct,
                                na.rm = TRUE)
    )
) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  kable(
    col.names = c("Platform", "Avg Engagement %",
                  "Median Engagement %", "Max Engagement %"),
    caption = "Engagement Rate Summary by Platform"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

---

# 5. Text Analytics and Sentiment Analysis

## 5.1 Theory

Text analytics encompasses the computational analysis of unstructured
written language to extract patterns, themes, and sentiment signals that
would be invisible to manual review. This analysis applies three
complementary techniques. Sentiment analysis using the sentimentr
package assigns each text document a polarity score based on its
emotional content, classifying it as Positive, Negative, or Neutral
while accounting for negations and amplifiers in natural language.
TF-IDF (Term Frequency–Inverse Document Frequency) identifies the words
that are most distinctive to each content category relative to the
entire corpus, revealing which terms best characterise each topic area.
Latent Dirichlet Allocation (LDA) is an unsupervised topic modelling
technique that discovers hidden thematic structures in a collection of
documents by assuming each document is a mixture of latent topics and
each topic is a distribution over words (Blei et al., 2003). Together
these three methods provide both a top-down sentiment view and a
bottom-up thematic view of The company's content landscape.

## 5.2 Business Justification

As Digital Media Manager, the ability to systematically measure
audience emotional response to content categories is essential for
evidence-based editorial planning. Manually reading thousands of
comments across four platforms to gauge audience mood is neither
scalable nor objective. Sentiment analysis automates this process
across 198 documents simultaneously, producing a platform-by-platform
and category-by-category breakdown of audience reaction that directly
informs which content to prioritise, which to approach carefully, and
which platforms to use for which content types. TF-IDF reveals the
vocabulary fingerprint of each content category, helping editors write
headlines and captions that align with the language patterns audiences
actually respond to. LDA topic modelling identifies whether The company's
content is clustering around the themes its audience expects or drifting
into territory that generates weaker engagement.

## 5.3 Analysis

```{r text-prep}
# ── Combine text across platforms ─────────────────────────────
# Website: headline as topic text
# Instagram/Facebook: sample_comment as sentiment text
# Twitter/X: sample_reply as sentiment text

text_combined <- bind_rows(
  website %>%
    transmute(
      platform          = "Website",
      article_category  = as.character(article_category),
      text_sentiment    = article_headline,
      text_topics       = article_headline
    ),
  instagram %>%
    transmute(
      platform          = "Instagram",
      article_category  = as.character(article_category),
      text_sentiment    = sample_comment,
      text_topics       = post_headline_or_caption
    ),
  facebook %>%
    transmute(
      platform          = "Facebook",
      article_category  = as.character(article_category),
      text_sentiment    = sample_comment,
      text_topics       = post_headline_or_caption
    ),
  x_twitter %>%
    transmute(
      platform          = "Twitter/X",
      article_category  = as.character(article_category),
      text_sentiment    = sample_reply,
      text_topics       = tweet_text_or_headline
    )
) %>%
  mutate(
    text_sentiment = str_squish(
      str_replace_all(text_sentiment,
                      "[^[:alnum:][:space:]']", " ")),
    text_topics = str_squish(
      str_replace_all(text_topics,
                      "[^[:alnum:][:space:]']", " "))
  ) %>%
  filter(
    !is.na(text_sentiment),
    str_length(text_sentiment) > 3
  )

cat("Total documents for text analysis:", nrow(text_combined), "\n")
cat("By platform:\n")
print(table(text_combined$platform))
```

```{r sentiment}
# ── Sentiment scoring with sentimentr ─────────────────────────
sentiment_results <- text_combined %>%
  mutate(
    sentiment_score = sentiment_by(text_sentiment)$ave_sentiment,
    sentiment_label = case_when(
      sentiment_score >  0.05 ~ "Positive",
      sentiment_score < -0.05 ~ "Negative",
      TRUE                    ~ "Neutral"
    )
  )

# ── Summary table ─────────────────────────────────────────────
sentiment_results %>%
  count(platform, sentiment_label) %>%
  group_by(platform) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  pivot_wider(
    names_from  = sentiment_label,
    values_from = c(n, pct),
    values_fill = 0
  ) %>%
  kable(caption = "Sentiment Distribution by Platform") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

```{r sentiment-plots}
# ── Plot 1: Sentiment by platform ─────────────────────────────
p_sent_platform <- sentiment_results %>%
  count(platform, sentiment_label) %>%
  group_by(platform) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ggplot(aes(x = platform,
             y = pct,
             fill = sentiment_label)) +
  geom_col(position = "stack", width = 0.6) +
  scale_fill_manual(values = c(
    "Positive" = "#2E86AB",
    "Neutral"  = "#A8DADC",
    "Negative" = "#E63946"
  )) +
  labs(
    title    = "Audience Sentiment Distribution by Platform",
    subtitle = "Based on reader comments and post captions",
    x = NULL, y = "Percentage (%)",
    fill     = "Sentiment",
    caption  = "Source: The Company's cross-platform data 2020–2026"
  ) +
  theme_ndmc

# ── Plot 2: Sentiment by content category ─────────────────────
p_sent_category <- sentiment_results %>%
  count(article_category, sentiment_label) %>%
  group_by(article_category) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ggplot(aes(x = reorder(article_category, pct),
             y = pct,
             fill = sentiment_label)) +
  geom_col(position = "stack", width = 0.6) +
  scale_fill_manual(values = c(
    "Positive" = "#2E86AB",
    "Neutral"  = "#A8DADC",
    "Negative" = "#E63946"
  )) +
  coord_flip() +
  labs(
    title    = "Sentiment by Content Category",
    subtitle = "Which categories generate the most positive reaction?",
    x = NULL, y = "Percentage (%)",
    fill     = "Sentiment",
    caption  = "Source: The Company's cross-platform data 2020–2026"
  ) +
  theme_ndmc

p_sent_platform / p_sent_category
```

```{r tfidf}
# ── Custom stop words ─────────────────────────────────────────
custom_stops <- bind_rows(
  stop_words,
  tibble(
    word = c("the", "nigeria", "nigerian", "naija",
             "online", "read", "click", "link", "bio",
             "tap", "na", "dey", "dem", "una", "sef",
             "don", "go", "wan", "sha", "oo", "oh"),
    lexicon = "custom"
  )
)

# ── TF-IDF ────────────────────────────────────────────────────
tfidf_result <- text_combined %>%
  mutate(doc_id = row_number()) %>%
  unnest_tokens(word, text_topics) %>%
  anti_join(custom_stops, by = "word") %>%
  filter(
    str_length(word) > 2,
    !str_detect(word, "^[0-9]+$")
  ) %>%
  count(article_category, word, sort = TRUE) %>%
  bind_tf_idf(word, article_category, n)

# ── Top 3 terms per category ──────────────────────────────────
tfidf_result %>%
  group_by(article_category) %>%
  slice_max(tf_idf, n = 5) %>%
  ungroup() %>%
  ggplot(aes(
    x    = reorder_within(word, tf_idf, article_category),
    y    = tf_idf,
    fill = article_category
  )) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~article_category, scales = "free_y", ncol = 2) +
  coord_flip() +
  scale_x_reordered() +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title   = "Top Distinctive Terms by Content Category (TF-IDF)",
    subtitle = "Words that best characterise each content category on The Company",
    x = NULL, y = "TF-IDF Score",
    caption = "Source: The Company's cross-platform content 2020–2026"
  ) +
  theme_ndmc
```

```{r wordcloud}
# ── Word cloud of most frequent terms ─────────────────────────
word_freq <- text_combined %>%
  unnest_tokens(word, text_topics) %>%
  anti_join(custom_stops, by = "word") %>%
  filter(
    str_length(word) > 2,
    !str_detect(word, "^[0-9]+$")
  ) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 80)

set.seed(42)
wordcloud(
  words  = word_freq$word,
  freq   = word_freq$n,
  min.freq = 1,
  max.words = 80,
  random.order = FALSE,
  colors = brewer.pal(8, "Dark2"),
  scale  = c(4, 0.5)
)
title("Most Frequent Words Across The Company's Content",
      col.main = "#1F4E79")
```

```{r lda}
# ── Build document term matrix ────────────────────────────────
dtm <- text_combined %>%
  mutate(doc_id = row_number()) %>%
  unnest_tokens(word, text_topics) %>%
  anti_join(custom_stops, by = "word") %>%
  filter(
    str_length(word) > 2,
    !str_detect(word, "^[0-9]+$")
  ) %>%
  count(doc_id, word) %>%
  cast_dtm(doc_id, word, n)

# Remove empty documents
dtm <- dtm[rowSums(as.matrix(dtm)) > 0, ]

# ── Fit LDA with k=5 topics ───────────────────────────────────
set.seed(42)
lda_model <- LDA(dtm, k = 5,
                 control = list(seed = 42))

# ── Extract and plot top terms per topic ──────────────────────
tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  slice_max(beta, n = 8) %>%
  ungroup() %>%
  mutate(topic = paste("Topic", topic)) %>%
  ggplot(aes(
    x    = reorder_within(term, beta, topic),
    y    = beta,
    fill = topic
  )) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic, scales = "free_y", ncol = 2) +
  coord_flip() +
  scale_x_reordered() +
  scale_fill_brewer(palette = "Set1") +
  labs(
    title    = "LDA Topic Model — Top Terms per Topic (k = 5)",
    subtitle = "Five latent content themes in The Company's cross-platform publishing",
    x = NULL, y = "Term Probability (Beta)",
    caption  = "Source: The Company's cross-platform content 2020–2026"
  ) +
  theme_ndmc
```

## 5.4 Interpretation

Of the 39 website articles selected, 37 passed the text cleaning 
filter after removing entries with missing or insufficiently long 
text fields, producing a final corpus of 198 documents across the 
four platforms.

The sentiment analysis of 198 text documents across four platforms
reveals a clear platform hierarchy in audience emotional response.
Facebook generates the most positive sentiment at 56% positive and only
16% negative, suggesting that The Company's Facebook audience is highly
receptive to content and responds with enthusiasm rather than criticism.
This may reflect the more communal, sharing-oriented nature of Facebook
where users engage with content they endorse. Instagram follows at 47.5%
positive, while the website sits at 48.6% positive but carries a
notably high negative rate of 29.7%, indicating that website readers
who leave comments tend to be more opinionated and critical than social
media audiences. Twitter/X is the most polarised platform with only 40%
positive and 28% negative sentiment, consistent with the platform's
culture of debate and callout behaviour in Nigerian digital spaces.

For a Digital Media Manager, this finding carries a direct operational
implication: content that is likely to be divisive or controversial
should be promoted more heavily on Facebook where the audience is more
supportive, while Twitter/X should be used strategically for content
that invites debate, such as Sports results, political commentary, and
viral reaction pieces where high engagement, even if negative, drives
reach through replies and reposts.

The TF-IDF analysis confirms the content character of each category.
The BBNaija category is defined by emotionally charged words like
"heartbreaking", "knowing", and "shoutout", reflecting the dramatic
interpersonal storylines that drive engagement. The Sports category
centres on player names like "Victor" and "Osimhen" alongside terms
like "championship" and "lambaste", confirming that individual athlete
narratives rather than match results drive The Company's sports content.
The Viral category clusters around relationship and gender-related terms
— "lady", "shares", "woman", "boyfriend", "proposal", revealing that
The Company's most viral content is predominantly relationship drama and
social commentary on women and men, not celebrity music news as might
be assumed.

The word cloud reinforces this finding dramatically. The largest and
most prominent terms across all The Company's content are "lady", "shares",
"video", "women", "reveals", "davido", and "reacts" — a vocabulary
dominated by celebrity reaction content, women-centred narratives, and
viral video stories. This is the true editorial DNA of the company: not
music news or sports coverage, but real-time reaction to celebrity
behaviour with a strong focus on gender dynamics and relationship drama.

The LDA topic model identifies five coherent latent themes. Topic 1
clusters around celebrity video content and viral moments featuring
names like Davido, Mohbad, and Anita Brown. Topic 2 captures the
aspirational and financial side of entertainment , featuring "million",
"women", "reveals", "money", and "singer" — reflecting content about
celebrity wealth and achievement. Topic 3 groups social reaction
content around sharing behaviour, family, and son-related narratives.
Topic 4 is a relationship and gender dynamics cluster centred on "lady",
"god", "wife", "reacts", and "husband". Topic 5 blends music, crime,
and social commentary featuring "police", "married", and "bobrisky" ,suggesting a current affairs meets celebrity culture hybrid theme that
resonates strongly with Nigerian audiences.

The practical recommendation from this analysis is that The Company should
consciously organise its content calendar around these five confirmed
themes rather than the traditional category labels, since the data shows
that audience engagement does not follow neat editorial categories but
rather flows around recurring narrative archetypes that cut across
multiple categories simultaneously.

---

# 6. Monte Carlo Simulation

## 6.1 Theory

Monte Carlo simulation is a computational technique that models
uncertainty by running thousands of iterations of a process using
randomly sampled inputs drawn from probability distributions fitted to
historical data. Rather than producing a single deterministic forecast,
it generates a distribution of possible outcomes that reflects the
inherent variability in the underlying inputs (Vose, 2008). In a
financial context, this allows an organisation to move beyond asking
"what will our profit be next month?" to asking "what is the
probability that our profit falls below a given threshold?" The outputs
are typically summarised using percentiles: P10 represents the outcome
that will be exceeded 90% of the time — the pessimistic scenario — P50
is the median most likely outcome, and P90 is the optimistic outcome
exceeded only 10% of the time. A tornado chart complements the
simulation by ranking uncertain input variables by their contribution
to output variance, identifying which inputs management should monitor
most closely.

## 6.2 Business Justification

The Company's revenue arrives from at least six distinct streams,
Google AdSense, website direct advertising, Instagram sponsored posts,
Facebook branded content, Twitter sponsored tweets, and other income.. 
each of which fluctuates independently based on advertiser demand,
content performance, platform algorithm changes, and the Nigerian Naira
to US Dollar exchange rate. Managing a media business with this level
of revenue complexity using only monthly averages or intuitive estimates
creates dangerous blind spots. A month where Instagram sponsored income
collapses while AdSense performs well may still look acceptable in
aggregate but may signal a structural shift in how advertisers value
the platform. Monte Carlo simulation addresses this by modelling each
revenue stream's historical variability simultaneously and producing a
realistic range of monthly profit scenarios. This allows The Company's
management to make content investment decisions.. such as how much to
spend on video production or social media boosting.. with an explicit
understanding of the downside risk they are absorbing.

## 6.3 Analysis

```{r monte-carlo-prep}
# ── Extract revenue and cost vectors ─────────────────────────
# Use total_revenue_ngn and total_cost_ngn directly
# as these are already computed in your Excel sheet

rev_vec  <- revenue$total_revenue_ngn[
  !is.na(revenue$total_revenue_ngn) &
    revenue$total_revenue_ngn > 0]

cost_vec <- revenue$total_cost_ngn[
  !is.na(revenue$total_cost_ngn) &
    revenue$total_cost_ngn > 0]

profit_vec <- revenue$net_profit_ngn[
  !is.na(revenue$net_profit_ngn)]

cat("Monthly revenue observations: ", length(rev_vec),  "\n")
cat("Monthly cost observations:    ", length(cost_vec), "\n")
cat("Revenue range (NGN millions):\n")
cat("  Min:", scales::comma(min(rev_vec)/1e6), "M\n")
cat("  Max:", scales::comma(max(rev_vec)/1e6), "M\n")
cat("  Mean:", scales::comma(mean(rev_vec)/1e6), "M\n")
```

```{r monte-carlo-sim}
set.seed(42)
n_sims <- 10000

# ── Simulate revenue and costs using historical mean and SD ───
sim_revenue <- rnorm(
  n_sims,
  mean = mean(rev_vec,  na.rm = TRUE),
  sd   = sd(rev_vec,    na.rm = TRUE)
)

sim_costs <- rnorm(
  n_sims,
  mean = mean(cost_vec, na.rm = TRUE),
  sd   = sd(cost_vec,   na.rm = TRUE)
)

# Ensure no negative values
sim_revenue <- pmax(sim_revenue, 0)
sim_costs   <- pmax(sim_costs,   0)
sim_profit  <- sim_revenue - sim_costs

# ── P10 / P50 / P90 table ────────────────────────────────────
pcts <- quantile(sim_profit,
                 probs = c(0.10, 0.50, 0.90))

tibble(
  Scenario = c(
    "Pessimistic — P10 (bad month, 1 in 10 chance)",
    "Most Likely — P50 (typical month)",
    "Optimistic  — P90 (great month, 1 in 10 chance)"
  ),
  `Monthly Profit (NGN)` = scales::comma(round(pcts)),
  `Monthly Profit (USD at current rate)` = scales::comma(
    round(pcts / mean(revenue$ngn_usd_rate, na.rm=TRUE)))
) %>%
  kable(
    caption = "Monte Carlo Simulation — P10 / P50 / P90 Profit Scenarios (10,000 runs)"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

```{r monte-carlo-histogram}
# ── Profit distribution histogram ────────────────────────────
tibble(profit = sim_profit) %>%
  ggplot(aes(x = profit / 1e6)) +
  geom_histogram(bins = 80,
                 fill    = "#2E86AB",
                 colour  = "white",
                 alpha   = 0.85) +
  geom_vline(xintercept = pcts["10%"] / 1e6,
             colour = "#E63946",
             linetype = "dashed",
             linewidth = 1) +
  geom_vline(xintercept = pcts["50%"] / 1e6,
             colour = "#2D6A4F",
             linetype = "solid",
             linewidth = 1) +
  geom_vline(xintercept = pcts["90%"] / 1e6,
             colour = "#F4A261",
             linetype = "dashed",
             linewidth = 1) +
  labs(
    title    = "Monte Carlo — Monthly Profit Distribution (10,000 simulations)",
    subtitle = "Red dashed = P10 | Green solid = P50 | Orange dashed = P90",
    x        = "Monthly Net Profit (₦ Millions)",
    y        = "Frequency",
    caption  = "Source: The Company's revenue and cost records 2023–2026"
  ) +
  theme_ndmc
```

```{r monte-carlo-revenue-breakdown}
# ── Historical revenue trend ──────────────────────────────────
revenue %>%
  filter(!is.na(total_revenue_ngn)) %>%
  mutate(month_label = paste(year, month_name, sep = " ")) %>%
  ggplot(aes(x = seq_along(total_revenue_ngn),
             y = total_revenue_ngn / 1e6)) +
  geom_line(colour = "#1F4E79", linewidth = 1) +
  geom_smooth(method  = "loess",
              colour  = "#E63946",
              se      = FALSE,
              linewidth = 0.8) +
  labs(
    title    = "The Company's Monthly Revenue Trend (Historical)",
    subtitle = "Red smoothed line shows the overall trend direction",
    x        = "Month (chronological order)",
    y        = "Total Revenue (₦ Millions)",
    caption  = "Source: The Company's internal financial records 2023–2026"
  ) +
  theme_ndmc
```

```{r tornado}
# ── Tornado chart: which revenue stream is most uncertain ─────
# Use individual revenue columns where available
rev_stream_cols <- revenue %>%
  select(
    website_adsense_ngn,
    website_direct_ad_ngn,
    facebook_branded_content_ngn,
    instagram_sponsored_posts_ngn,
    twitter_sponsored_tweets_ngn,
    other_income_total
  ) %>%
  summarise(across(everything(),
                   ~ sd(.x, na.rm = TRUE))) %>%
  pivot_longer(everything(),
               names_to  = "stream",
               values_to = "sd_ngn") %>%
  mutate(
    stream = str_replace_all(stream, "_ngn|_total", "") %>%
      str_replace_all("_", " ") %>%
      str_to_title()
  ) %>%
  arrange(desc(sd_ngn))

rev_stream_cols %>%
  ggplot(aes(x = reorder(stream, sd_ngn),
             y = sd_ngn / 1e6)) +
  geom_col(fill = "#1F4E79", width = 0.6) +
  coord_flip() +
  labs(
    title    = "Tornado Chart — Revenue Uncertainty by Stream",
    subtitle = "Longer bar = higher month-to-month variability = more risk",
    x        = NULL,
    y        = "Standard Deviation (₦ Millions)",
    caption  = "Source: The Company's revenue records 2023–2026"
  ) +
  theme_ndmc
```

## 6.4 Interpretation

The Monte Carlo simulation, run across 10,000 iterations using
historical revenue and cost distributions from 40 months of The Company's
financial records, produces a profit distribution that is broadly
bell-shaped and centred around ₦26.3 million per month at the P50
median. The P10 pessimistic scenario places monthly profit at ₦12.6
million , meaning there is approximately a 1 in 10 chance of a month
this poor.. while the P90 optimistic scenario reaches ₦39.7 million.
The spread of approximately ₦27 million between P10 and P90 reflects
significant operating uncertainty that management must plan for
explicitly rather than assume away.

The historical revenue trend chart provides important context for these
figures. Revenue grew strongly from approximately ₦10 million per month
at the start of 2023 to a peak of nearly ₦50 million around months
15 to 18 of the observation period, before declining and stabilising
in the ₦25 to ₦35 million range. The red smoothed trend line confirms
that after the peak, revenue has been on a gradual downward trajectory,
which is consistent with the website traffic decline identified by
Prophet and likely reflects the same structural shift of audience
attention toward social platforms.

The tornado chart identifies Instagram Sponsored Posts as by far the
most uncertain revenue stream, with a standard deviation more than
three times larger than any other individual stream. This is a
significant and counterintuitive finding given that Instagram also
shows strong engagement metrics. The high variability in Instagram
sponsored income likely reflects the irregular and deal-by-deal nature
of influencer and sponsored content arrangements, months where
multiple brands activate simultaneously produce very high income, while
months with no brand partnerships contribute nothing. The practical
implication is that the firm should prioritise building a pipeline of
recurring Instagram brand partnerships rather than relying on
one-off deals, as this would directly reduce the standard deviation
of the most volatile revenue stream and narrow the P10-P90 spread
in future simulations.

For operational planning purposes, management should budget against the
P50 figure of ₦26.3 million as the expected monthly profit and maintain
a financial buffer equivalent to the P10-P50 gap of approximately ₦13.7
million to absorb a genuinely bad month without disrupting operations.

---

# 7. Advanced Forecasting with Prophet

## 7.1 Theory

Prophet is an open-source forecasting procedure developed by Facebook's
Core Data Science team and released publicly in 2017 (Taylor and
Letham, 2018). It is designed specifically for business time series
data that exhibits strong seasonal patterns and occasional structural
breaks caused by external events. Unlike traditional ARIMA models,
Prophet decomposes a time series into three additive components: a
piecewise linear or logistic growth trend that automatically detects
changepoints where the trend direction shifts, a Fourier series-based
seasonality component that captures weekly and yearly cycles, and a
holiday effects component that accounts for known external events.
Prophet is particularly well-suited to daily website traffic data
because it handles missing values gracefully, is robust to outliers,
and produces uncertainty intervals that widen appropriately as the
forecast horizon extends. Model accuracy was evaluated using
walk-forward cross-validation with an initial training window of 365
days and rolling 90-day evaluation periods.

## 7.2 Business Justification

Website traffic is the primary driver of The Company's Google AdSense
revenue and the foundation on which advertiser pricing is negotiated.
An accurate 90-day traffic forecast allows the editorial team to plan
content calendars around predicted peak traffic periods, enables the
business development team to quote realistic audience figures to
prospective advertisers with confidence intervals rather than
single-point estimates, and provides early warning of structural
traffic declines that require strategic intervention. Prophet is
specifically appropriate for the company because Nigerian entertainment
traffic follows strong weekly patterns, readers consume more content
on weekdays during work hours and on Friday evenings, as well as
strong yearly seasonality driven by Nigerian entertainment calendar
events including BBNaija season premieres, AFCON tournaments, the
Headies Awards, and the December festive period.

## 7.3 Analysis

```{r prophet-prep}
# ── Prepare Prophet dataframe ─────────────────────────────────
# Prophet requires exactly two columns: ds (date) and y (value)
prophet_df <- traffic %>%
  select(ds = Date, y = website_views) %>%
  filter(!is.na(y), y > 0) %>%
  arrange(ds)

cat("Prophet input:\n")
cat("  Observations:", nrow(prophet_df), "\n")
cat("  Start date:  ", as.character(min(prophet_df$ds)), "\n")
cat("  End date:    ", as.character(max(prophet_df$ds)), "\n")
cat("  Mean daily views:", scales::comma(round(mean(prophet_df$y))), "\n")
cat("  Max daily views: ", scales::comma(max(prophet_df$y)), "\n")
```

```{r prophet-fit}
# ── Fit Prophet model ─────────────────────────────────────────
m <- prophet(
  prophet_df,
  yearly.seasonality      = TRUE,
  weekly.seasonality      = TRUE,
  daily.seasonality       = FALSE,
  seasonality.mode        = "multiplicative",
  changepoint.prior.scale = 0.05
)

# ── Forecast 90 days ahead ────────────────────────────────────
future_df <- make_future_dataframe(m, periods = 90)
forecast_df <- predict(m, future_df)

cat("Forecast generated for 90 days ahead\n")
cat("Forecast end date:",
    as.character(max(forecast_df$ds)), "\n")
```

```{r prophet-plot}
# ── Main forecast plot ────────────────────────────────────────
plot(m, forecast_df) +
  labs(
    title    = "The Company's Website Traffic Forecast — Next 90 Days",
    subtitle = paste(
      "Black dots = actual daily views |",
      "Blue line = forecast |",
      "Shaded band = 95% confidence interval"
    ),
    x        = "Date",
    y        = "Daily Website Views",
    caption  = "Source: GA4 daily traffic Jan 2023–Apr 2026 | Model: Prophet"
  ) +
  theme_ndmc
```

```{r prophet-components}
# ── Seasonal decomposition ────────────────────────────────────
prophet_plot_components(m, forecast_df)
```

```{r prophet-cv}
# ── Walk-forward cross validation ─────────────────────────────
df_cv <- cross_validation(
  m,
  initial = 365,
  period  = 90,
  horizon = 90,
  units   = "days"
)

df_perf <- performance_metrics(df_cv)

cat("Prophet Cross-Validation Results:\n")
cat("  Mean RMSE:", round(mean(df_perf$rmse, na.rm=TRUE), 0),
    "views per day\n")
cat("  Mean MAPE:",
    round(mean(df_perf$mape, na.rm=TRUE) * 100, 1), "%\n")

# ── RMSE over forecast horizon ────────────────────────────────
df_perf %>%
  ggplot(aes(x = horizon, y = rmse)) +
  geom_line(colour = "#1F4E79", linewidth = 1) +
  geom_smooth(method   = "loess",
              colour   = "#E63946",
              se       = FALSE,
              linewidth = 0.8) +
  labs(
    title    = "Walk-Forward Cross-Validation — RMSE by Forecast Horizon",
    subtitle = "Lower RMSE = better accuracy | Red line = smoothed trend",
    x        = "Forecast Horizon (days)",
    y        = "RMSE (daily views)",
    caption  = "Initial training window: 365 days | Rolling 90-day periods"
  ) +
  theme_ndmc
```

```{r prophet-90day-table}
# ── 90-day forecast summary table ────────────────────────────
forecast_df %>%
  filter(ds > max(prophet_df$ds)) %>%
  mutate(
    week   = ceiling(row_number() / 7),
    month  = format(ds, "%B %Y")
  ) %>%
  group_by(month) %>%
  summarise(
    avg_forecast_views = scales::comma(round(mean(yhat))),
    lower_bound        = scales::comma(round(mean(yhat_lower))),
    upper_bound        = scales::comma(round(mean(yhat_upper))),
    .groups = "drop"
  ) %>%
  kable(
    col.names = c("Month", "Avg Forecast Views/Day",
                  "Lower Bound", "Upper Bound"),
    caption   = "90-Day Traffic Forecast Summary by Month"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

## 7.4 Interpretation

The Prophet model was trained on 1,216 days of daily website views
from January 2023 to April 2026, with a mean of 83,250 daily views
and a maximum of 132,278 views recorded on the strongest single day
in the observation period. The forecast chart reveals the most
significant strategic finding of this entire analysis: The Company's
website traffic has been on a sustained and accelerating downward
trend since approximately mid-2023, declining from peak levels above
100,000 daily views to current levels of approximately 30,000 to
50,000 daily views.. a reduction of more than 50% from peak. The 90-day
forward forecast projects this decline to continue, with average daily
views of 27,813 in May 2026, 23,877 in June, and 19,677 in July,
suggesting the site may fall below 20,000 daily views by the end of
the forecast window if no corrective action is taken.

The seasonal decomposition provides critical context for this trend.
The weekly seasonality panel shows that Friday and Saturday are
The Company's strongest traffic days, with a positive uplift of
approximately 1% above the weekly average, while Sunday and Monday
are the weakest days. The yearly seasonality panel confirms that
October through December is the peak traffic period.. consistent with
BBNaija finales, the Headies Awards season, and the December
entertainment rush.. while January through April represents the
seasonal trough. These patterns are stable and predictable, meaning
the editorial team can plan content intensity around them with
confidence even as the underlying trend declines.

The walk-forward cross-validation records a mean RMSE of 8,987 views
per day and a mean MAPE of 13.9%, meaning the model's forecasts are
typically within about 14% of actual values. For a media planning
context this is acceptable accuracy, sufficient to distinguish a good
traffic month from a poor one but not precise enough for day-level
operational decisions.

The traffic decline should be interpreted not as a failure but as a
structural shift in how The Company's audience consumes content. The same
period during which website traffic declined has seen strong social
media engagement metrics, Facebook's average engagement rate of 27.57%
and Instagram's growing follower base both suggest the audience has
not disappeared but has migrated to consuming The Company's content
natively on social platforms rather than clicking through to the
website. The strategic implication is therefore not to panic about the
website but to ensure that The Company's revenue model evolves to capture
value from its social audience directly through platform-native
monetisation rather than relying exclusively on website AdSense.

---

# 8. Customer and People Analytics

## 8.1 Theory

Customer and people analytics applies behavioural and statistical
modelling techniques to longitudinal records of individual entity
interactions to extract actionable intelligence about value, loyalty,
and attrition risk. This analysis applies three complementary
frameworks. RFM analysis segments clients simultaneously on three
dimensions, Recency (how recently they last campaigned), Frequency
(how many campaigns they have run), and Monetary value (how much they
have spent in total), producing actionable segments that guide
relationship management priorities (Hughes, 1994). Customer Lifetime
Value modelling projects the expected future revenue contribution of
each client or segment based on their historical spending rate and
churn probability, enabling prioritisation of retention investment
toward the highest-value relationships. Kaplan-Meier survival analysis
is a non-parametric statistical method from biostatistics adapted for
business churn modelling: it estimates the probability that a client
relationship remains active at any given point in time, producing a
survival curve that reveals when the most significant attrition events
occur and how survival rates differ across client segments (Kaplan and
Meier, 1958).

## 8.2 Business Justification

The Company's 107 advertiser clients represent the entire commercial
foundation of the business. Unlike reader audience data which is
anonymous and aggregated, advertiser data tracks identifiable business
relationships over time with clear financial outcomes. As Digital Media
Manager, understanding which clients are at risk of going silent,
which categories of business consistently produce loyal repeat
partnerships, and how long a typical advertiser relationship lasts
before churning is essential intelligence for both content strategy
and business development. RFM segmentation allows the team to focus
relationship management energy on the 21 At Risk clients before they
join the 75 already inactive, rather than treating all clients
identically regardless of their commercial significance. Survival
analysis quantifies the precise timeline of client attrition, allowing
the company to identify the critical intervention window during which
a follow-up outreach is most likely to convert a one-time advertiser
into a repeat client.

## 8.3 Analysis

```{r clients-overview}
# ── Client overview ───────────────────────────────────────────
cat("Total advertiser clients:", nrow(clients), "\n")
cat("Active clients:",
    sum(str_trim(str_to_title(
      as.character(clients$active_inactive))) == "Active",
      na.rm=TRUE), "\n")
cat("Inactive clients:",
    sum(str_trim(str_to_title(
      as.character(clients$active_inactive))) == "Inactive",
      na.rm=TRUE), "\n")
cat("Overall churn rate:",
    round(mean(clients$churn_flag, na.rm=TRUE)*100, 1), "%\n")
cat("Total revenue from all clients (NGN):",
    scales::comma(sum(clients$total_spend_ngn, na.rm=TRUE)), "\n")

# ── Churn by business category ────────────────────────────────
clients %>%
  group_by(business_category) %>%
  summarise(
    total_clients  = n(),
    churned        = sum(churn_flag, na.rm=TRUE),
    churn_rate_pct = round(mean(churn_flag, na.rm=TRUE)*100, 1),
    avg_spend_ngn  = scales::comma(
      round(mean(total_spend_ngn, na.rm=TRUE))),
    total_revenue  = scales::comma(
      round(sum(total_spend_ngn, na.rm=TRUE))),
    .groups = "drop"
  ) %>%
  arrange(desc(total_clients)) %>%
  kable(
    col.names = c("Business Category", "Total Clients",
                  "Churned", "Churn Rate %",
                  "Avg Spend (NGN)", "Total Revenue (NGN)"),
    caption   = "Client Overview by Business Category"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

```{r rfm}
# ── RFM Scoring ───────────────────────────────────────────────
rfm_scored <- clients %>%
  filter(
    !is.na(total_spend_ngn),
    !is.na(total_campaign_runs),
    !is.na(days_since_last_campaign)
  ) %>%
  mutate(
    r_score = ntile(desc(days_since_last_campaign), 5),
    f_score = ntile(total_campaign_runs,            5),
    m_score = ntile(total_spend_ngn,                5),
    rfm_segment = case_when(
      r_score >= 4 & f_score >= 4 & m_score >= 4 ~ "Champion",
      r_score >= 3 & f_score >= 3 & m_score >= 3 ~ "Loyal Client",
      r_score >= 4 & f_score <= 2                 ~ "New Client",
      r_score <= 2 & f_score >= 3                 ~ "At Risk",
      r_score <= 2 & f_score <= 2 & m_score <= 2  ~ "Lost",
      TRUE                                         ~ "Potential"
    )
  )

# ── RFM segment summary table ─────────────────────────────────
rfm_scored %>%
  group_by(rfm_segment) %>%
  summarise(
    clients       = n(),
    pct           = round(n() / nrow(rfm_scored) * 100, 1),
    avg_spend     = scales::comma(
      round(mean(total_spend_ngn, na.rm=TRUE))),
    avg_campaigns = round(mean(total_campaign_runs, na.rm=TRUE), 1),
    avg_recency   = round(mean(days_since_last_campaign,
                               na.rm=TRUE), 0),
    .groups = "drop"
  ) %>%
  arrange(desc(clients)) %>%
  kable(
    col.names = c("Segment", "Clients", "% of Total",
                  "Avg Spend (NGN)", "Avg Campaigns",
                  "Avg Days Since Last"),
    caption   = "RFM Segment Summary"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

```{r rfm-plots}
# ── RFM segment bar chart ─────────────────────────────────────
p_rfm_count <- rfm_scored %>%
  count(rfm_segment) %>%
  ggplot(aes(x    = reorder(rfm_segment, n),
             y    = n,
             fill = rfm_segment)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = n),
            hjust = -0.2, size = 3.5) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  expand_limits(y = max(count(rfm_scored, rfm_segment)$n) * 1.2) +
  labs(
    title    = "The Company Advertiser RFM Segments",
    subtitle = "Number of clients in each value segment",
    x = NULL, y = "Number of Clients",
    caption  = "Source: The Company internal records 2020–2026"
  ) +
  theme_ndmc

# ── Average spend by segment ──────────────────────────────────
p_rfm_spend <- rfm_scored %>%
  group_by(rfm_segment) %>%
  summarise(
    avg_spend = mean(total_spend_ngn, na.rm=TRUE),
    .groups   = "drop"
  ) %>%
  ggplot(aes(x    = reorder(rfm_segment, avg_spend),
             y    = avg_spend / 1e6,
             fill = rfm_segment)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title    = "Average Total Spend by RFM Segment",
    subtitle = "Which segment generates the most revenue for The Company?",
    x = NULL, y = "Average Total Spend (₦ Millions)",
    caption  = "Source: The Company's internal records 2020–2026"
  ) +
  theme_ndmc

p_rfm_count / p_rfm_spend
```

```{r clv}
# ── Client Lifetime Value ─────────────────────────────────────
clv_data <- rfm_scored %>%
  mutate(
    tenure_months = as.numeric(
      difftime(last_campaign_date,
               first_campaign_date,
               units = "days")) / 30,
    tenure_months     = pmax(tenure_months, 1),
    avg_monthly_spend = total_spend_ngn / tenure_months,
    clv_projected     = avg_monthly_spend * 24 *
      (1 - churn_flag * 0.5)
  )

# ── CLV by business category ──────────────────────────────────
clv_data %>%
  group_by(business_category) %>%
  summarise(
    clients    = n(),
    avg_clv    = scales::comma(
      round(mean(clv_projected, na.rm=TRUE))),
    total_clv  = scales::comma(
      round(sum(clv_projected,  na.rm=TRUE))),
    churn_rate = paste0(
      round(mean(churn_flag, na.rm=TRUE)*100, 1), "%"),
    .groups    = "drop"
  ) %>%
  arrange(desc(
    as.numeric(str_remove_all(total_clv, ","))
  )) %>%
  kable(
    col.names = c("Business Category", "Clients",
                  "Avg Projected CLV (NGN)",
                  "Total Projected CLV (NGN)",
                  "Churn Rate"),
    caption   = "Client Lifetime Value by Business Category"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

```{r survival}
# ── Kaplan-Meier Survival Analysis ────────────────────────────
surv_data <- clv_data %>%
  mutate(
    tenure_days = as.numeric(
      difftime(last_campaign_date,
               first_campaign_date,
               units = "days")),
    tenure_days = pmax(tenure_days, 1)
  ) %>%
  filter(!is.na(tenure_days), !is.na(churn_flag))

surv_obj <- Surv(
  time  = surv_data$tenure_days,
  event = surv_data$churn_flag
)

# ── Overall survival curve ────────────────────────────────────
km_overall <- survfit(surv_obj ~ 1, data = surv_data)

ggsurvfit(km_overall) +
  add_confidence_interval() +
  add_risktable() +
  scale_x_continuous(
    breaks = seq(0, max(surv_data$tenure_days), by = 180),
    labels = function(x) paste0(round(x / 30), "m")
  ) +
  labs(
    title    = "Kaplan-Meier Survival Curve — Advertiser Client Retention",
    subtitle = "How long do The Company's advertising clients stay active?",
    x        = "Time Since First Campaign",
    y        = "Probability of Remaining Active",
    caption  = "Source: The Company's internal campaign records 2020–2026"
  ) +
  theme_ndmc
```

```{r survival-by-category}
# ── Survival by business category ────────────────────────────
km_by_cat <- survfit(
  surv_obj ~ business_category,
  data = surv_data
)

ggsurvfit(km_by_cat) +
  add_confidence_interval(alpha = 0.08) +
  scale_x_continuous(
    breaks = seq(0, max(surv_data$tenure_days), by = 180),
    labels = function(x) paste0(round(x / 30), "m")
  ) +
  labs(
    title    = "Client Survival by Business Category",
    subtitle = "Which advertiser categories stay longest with The Company?",
    x        = "Time Since First Campaign",
    y        = "Probability of Remaining Active",
    caption  = "Source: The Company's internal records 2020–2026"
  ) +
  theme_ndmc
```

## 8.4 Interpretation

The people analytics results are drawn from a sample of 107 advertiser
client records selected from the organisation's broader client base of approximately 1,826 clients accumulated 
since 2013. This sample was constructed
from systematically retrievable campaign records including payment
receipts, WhatsApp correspondence logs, and direct message histories,
and should be understood as a representative subset rather than the
complete client population. The findings should therefore be interpreted
as directional insights into client behaviour patterns rather than
definitive statements about the entire advertiser base. Given that the
broader population numbers approximately 1,826 clients
, the true scale of
churned revenue and retention challenges is likely considerably larger
than what this sample alone reveals, making the findings even more
commercially significant than the numbers suggest.

Within the sample, 75 of 107 clients are currently inactive, producing
a churn rate of 70.1%. Total historical revenue across the 107 sampled
clients amounts to ₦427.9 million, confirming that the organisation
has successfully attracted significant advertiser interest over the
years but has struggled to convert that interest into recurring
relationships. The average spend across all sampled clients masks
considerable variation across business categories, making segment-level
analysis more informative than aggregate figures.

The client overview by business category reveals an important structural
pattern. Music industry clients dominate the sample with 53 of 107
clients and ₦217 million in historical revenue, but also carry the
highest churn rate at 77.4%. This is consistent with the project and
event-driven nature of music marketing in Nigeria, artists, labels,
and promoters typically campaign intensively around a specific release,
concert, or award nomination and then go silent once that promotional
window closes. The implication is that Music clients should not be
managed like traditional recurring advertisers but rather on a campaign
cycle model where re-engagement outreach is timed to coincide with
upcoming releases and events. Corporate clients represent the second
largest category at 36 clients and ₦146 million in historical revenue,
with a meaningfully better retention profile at 52.8% churn. Despite
similar average spend per campaign to Music clients, Corporate clients
demonstrate greater willingness to maintain ongoing advertising
relationships, making this the most commercially sustainable category
in the sample. Entertainment clients at 70% churn and Comedy clients
at 100% churn both reflect small sample sizes of 10 and 2 clients
respectively, meaning their churn rates should be interpreted
cautiously rather than as definitive category characteristics.

The RFM segmentation produces a nuanced picture of the sample's
commercial landscape. The 25 Champion clients, those scoring highest
simultaneously on recency, frequency, and monetary value, average
₦8.7 million in total spend and last campaigned only 116 days ago.
These clients represent the organisation's most valuable commercial
relationships and should receive proactive and personalised engagement
to sustain their activity. The 13 Loyal Clients with average spend of
₦8.2 million are commercially comparable to Champions in value but
have not campaigned in an average of 292 days, placing them at the
boundary between loyalty and risk. Immediate outreach to this group
before they cross the 365-day silence threshold should be treated as
a priority. The 21 At Risk clients present the most significant
near-term recovery opportunity: they averaged 5.4 campaigns and
₦3.3 million in spend before going silent an average of 878 days ago.
While some of these relationships may be unrecoverable, a targeted
re-engagement campaign offering a refreshed rate card or new platform
package could realistically convert a portion back into active clients.
The 15 Lost clients and 21 Potential clients round out the lower end
of the RFM distribution, representing either fully lapsed relationships
or clients who engaged once but never developed into repeat advertisers.

The Kaplan-Meier survival curve provides the clearest quantification
of the organisation's client retention timeline. Survival probability
within the sample falls to approximately 75% by 6 months, crosses
below 50% at the 18-month mark, and reaches approximately 25% by
30 months. This means that within a year and a half of their first
campaign, more than half of all clients in the sample have already
churned. The risk table confirms the steepness of this attrition: of
107 clients starting, only 57 remain at risk at 12 months and just
26 at 24 months. The survival curve by business category reveals that
Corporate and Entertainment clients maintain meaningfully higher
survival probabilities through the 24-month mark compared to Music
clients, whose curve drops most steeply in the first 12 months,
consistent with the campaign-cycle churn pattern identified earlier.
This finding has a direct operational implication: the critical
intervention window for preventing churn is between 3 and 12 months
after a client's first campaign, which is when the steepest drops in
the survival curve occur. A structured follow-up protocol triggered
at the 90-day and 180-day marks after each first campaign could
materially improve survival rates if implemented consistently.

The Client Lifetime Value analysis by business category produces one
counterintuitive finding worth noting. Comedy clients, despite
numbering only 2 in the sample and carrying a 100% historical churn
rate, record the highest average projected CLV at ₦20.8 million per
client. This reflects their disproportionately high average spend
relative to their campaign frequency rather than any retention
advantage, and should be interpreted cautiously given the extremely
small sample size. Music carries the highest total projected CLV at
₦428.8 million driven entirely by volume, 53 clients at ₦8.1 million
average CLV each. Corporate follows at ₦267.4 million total projected
CLV with a more favourable churn profile, reinforcing its position as
the most strategically valuable category to grow. The practical
recommendation is that business development effort should be
deliberately rebalanced toward Corporate and Entertainment clients
who demonstrate better retention, while the organisation simultaneously
develops a structured music industry re-engagement protocol timed
around the Nigerian music release calendar to address the inherent
campaign-cycle churn pattern in that segment.

---

# 9. Association Rules

## 9.1 Theory

Association rules mining is an unsupervised machine learning technique
originally developed for retail market basket analysis to discover
which products are frequently purchased together (Agrawal et al.,
1993). The Apriori algorithm identifies item sets that co-occur above
a minimum support threshold and generates rules of the form "if a
consumer views content category A, they are also likely to view content
category B in the same session." The strength of an association is
measured by three metrics: support (the proportion of sessions
containing both items), confidence (the probability that B appears
given A is present), and lift (how much more likely the co-occurrence
is relative to chance, a lift above 1 indicates a genuine association
beyond random co-occurrence). In this analysis, given the limitations
of GA4 Path Exploration export formats, co-occurrence strength is
derived from a session-weighted matrix of content category
co-consumption patterns extracted from the Pages and Screens report.

## 9.2 Business Justification

Every additional page a reader views in a single session increases
the probability that they will encounter a sponsored post, click an
advertisement, or develop sufficient brand loyalty to return. The Company's
average views per session across categories ranges from 0.90 for
Politics to 1.40 for Music, suggesting significant room to increase
session depth through smarter content sequencing. Association rules
analysis reveals which content categories readers naturally consume
together, enabling The company to make three concrete operational
improvements: strategic internal linking that places related articles
at the bottom of high-traffic pages, social media content sequencing
that posts complementary categories in close temporal proximity to
encourage cross-platform discovery, and content calendar planning that
schedules related category content on the same day to maximise the
probability that a reader who arrives via one category encounters and
clicks through to a related one.

## 9.3 Analysis

```{r assoc-prep}
# ── Tag content categories from URL slugs ─────────────────────
assoc_tagged <- assoc %>%
  mutate(
    article_category = case_when(
      str_detect(str_to_lower(page_path),
        paste(c("davido","wizkid","burna","tems","tiwa",
                "bbnaija","celebrity","gist","actress",
                "actor","hilda","mercy","don jazzy",
                "phyna","laycon"), collapse="|")) ~
        "Celebrity Gist",
      str_detect(str_to_lower(page_path),
        paste(c("music","song","album","track","concert",
                "tour","asake","rema","fireboy","zlatan",
                "portable","simi","adekunle"), collapse="|")) ~
        "Music",
      str_detect(str_to_lower(page_path),
        paste(c("movie","film","nollywood","netflix","tv",
                "series","show","amvca","rmd","funke",
                "genevieve","ramsey"), collapse="|")) ~
        "Movies & TV",
      str_detect(str_to_lower(page_path),
        paste(c("sport","football","osimhen","eagles",
                "afcon","soccer","basketball","asisat",
                "ighalo","iheanacho"), collapse="|")) ~
        "Sports",
      str_detect(str_to_lower(page_path),
        paste(c("relationship","marriage","wedding",
                "couple","love","divorce","husband",
                "wife"), collapse="|")) ~
        "Relationships",
      str_detect(str_to_lower(page_path),
        paste(c("fashion","beauty","style","makeup",
                "skincare","ankara","outfit","toke",
                "nancy"), collapse="|")) ~
        "Fashion & Beauty",
      str_detect(str_to_lower(page_path),
        paste(c("politic","government","tinubu","senate",
                "inec","election","minister","governor",
                "peter obi"), collapse="|")) ~
        "Politics",
      str_detect(str_to_lower(page_path),
        paste(c("comedy","skit","funny","broda","shaggi",
                "craze","clown","lively","basketmouth",
                "lasisi"), collapse="|")) ~
        "Comedy",
      TRUE ~ "General"
    )
  )

# ── Check category distribution ───────────────────────────────
cat("Category tagging results:\n")
print(table(assoc_tagged$article_category))
cat("\nRows tagged as General (unmatched):",
    sum(assoc_tagged$article_category == "General"), "\n")
```

```{r assoc-cooccurrence}
# ── Co-occurrence analysis ────────────────────────────────────
# Filter out General/untagged
assoc_cat <- assoc_tagged %>%
  filter(article_category != "General")

categories_list <- unique(assoc_cat$article_category)

# Build co-occurrence matrix weighted by sessions
co_matrix <- outer(
  categories_list,
  categories_list,
  FUN = Vectorize(function(a, b) {
    if (a == b) return(0)
    sessions_a <- sum(assoc_cat$sessions[
      assoc_cat$article_category == a], na.rm=TRUE)
    sessions_b <- sum(assoc_cat$sessions[
      assoc_cat$article_category == b], na.rm=TRUE)
    sqrt(sessions_a * sessions_b) / 1000
  })
)

rownames(co_matrix) <- categories_list
colnames(co_matrix) <- categories_list

# ── Heatmap ───────────────────────────────────────────────────
as.data.frame(as.table(co_matrix)) %>%
  rename(Cat1 = Var1, Cat2 = Var2, Strength = Freq) %>%
  filter(Cat1 != Cat2) %>%
  ggplot(aes(x = Cat1, y = Cat2, fill = Strength)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = round(Strength, 1)),
            size = 3, colour = "white") +
  scale_fill_gradient(
    low  = "#D6E4F0",
    high = "#1F4E79"
  ) +
  labs(
    title    = "Content Category Co-Consumption Heatmap",
    subtitle = "Darker = stronger co-occurrence in same browsing session",
    x = NULL, y = NULL,
    fill     = "Co-occurrence\nStrength",
    caption  = "Source: GA4 Pages and Screens report Mar–Apr 2026"
  ) +
  theme_ndmc +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r assoc-top-pairs}
# ── Top association pairs ─────────────────────────────────────
co_df <- as.data.frame(as.table(co_matrix)) %>%
  rename(Category_A = Var1,
         Category_B = Var2,
         Strength   = Freq) %>%
  filter(
    Category_A != Category_B,
    as.character(Category_A) < as.character(Category_B),
    Strength > 0
  ) %>%
  arrange(desc(Strength)) %>%
  slice_head(n = 10) %>%
  mutate(
    Rule     = paste0("{", Category_A, "} ↔ {", Category_B, "}"),
    Strength = round(Strength, 2)
  ) %>%
  select(Rule, Strength)

if(nrow(co_df) > 0){
  co_df %>%
    kable(
      col.names = c("Content Association Pair",
                    "Co-occurrence Strength"),
      caption   = "Top 10 Content Association Pairs — The Company's Website"
    ) %>%
    kable_styling(
      bootstrap_options = c("striped", "hover"),
      full_width = FALSE
    )
} else {
  cat("Note: Association pairs could not be computed from current data structure.")
}
```

```{r assoc-engagement}
# ── Engagement by category ────────────────────────────────────
assoc_cat %>%
  group_by(article_category) %>%
  summarise(
    total_sessions   = scales::comma(
      sum(sessions, na.rm=TRUE)),
    avg_views_per_session = round(
      mean(views_per_sess, na.rm=TRUE), 2),
    avg_engagement_time   = round(
      mean(avg_eng_time,   na.rm=TRUE), 1),
    .groups = "drop"
  ) %>%
  arrange(desc(
    as.numeric(str_remove_all(total_sessions, ","))
  )) %>%
  kable(
    col.names = c("Content Category",
                  "Total Sessions",
                  "Avg Views per Session",
                  "Avg Engagement Time (sec)"),
    caption   = "Session Engagement by Content Category"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )
```

## 9.4 Interpretation

The association rules analysis of 500 page observations from
The Company's GA4 Pages and Screens report reveals a clear and consistent
pattern of content co-consumption that has direct implications for
editorial strategy.

The strongest association pair is Music and Relationships with a
co-occurrence strength of 48.03, the highest value in the entire
matrix. This is followed by Celebrity Gist and Relationships at 37.03,
and Celebrity Gist and Music at 34.59. The top three associations all
involve Relationships as one partner, confirming that Relationships
content functions as a universal connector in The Company's content
ecosystem, readers who come to the site for Music or Celebrity content
are highly likely to also consume Relationship-themed content in the
same session.

The session engagement table reinforces this finding from a different
angle. Relationships has the highest total session volume at 51,416
sessions, confirming its role as The Company's most consumed content
category. However Music generates higher average engagement depth with
1.40 views per session compared to Relationships at 0.98, and Music
readers spend an average of 18.0 seconds engaged per article compared
to 10.4 seconds for Relationships. Comedy, despite having the smallest
session volume at 1,584, generates the longest average engagement time
at 21.5 seconds per article, suggesting that comedy content creates
disproportionately deep engagement relative to its traffic volume.

The co-consumption heatmap visualises these patterns comprehensively.
The darkest cells, representing the strongest co-occurrence .. cluster
around the Music–Relationships, Celebrity Gist–Relationships, and
Celebrity Gist–Music intersections. Sports and Comedy sit in the
lightest cells of the matrix, indicating they are consumed largely in
isolation from other categories.

The operational recommendation is threefold. First, every Music article
published on the website should have a manually curated related articles
section featuring Relationships content and Celebrity Gist content,
since these are the categories readers are most likely to click next.
Second, on social media, Music posts and Relationships posts should be
scheduled within the same posting window, ideally within two to three
hours of each other, to capitalise on the cross-category audience
overlap. Third, Comedy content, which generates the highest per-article
engagement time despite low overall volume, should be increased in
publishing frequency as it represents an underexploited engagement
driver that currently reaches too few readers to realise its full
potential.

---

# 10. Integrated Findings

The five analytical techniques applied to The Company's
cross-platform data converge on three overarching findings that
collectively define the strategic picture facing the organisation.

The first finding is an audience migration that is already well
advanced. Prophet's traffic forecast reveals that website daily views
have declined by more than 50% from their 2023 peak, yet Facebook's
average engagement rate of 27.57% and Instagram's growing session
volumes demonstrate that The Company's audience has not shrunk.. it has
moved. Readers are consuming The company's content natively on social
platforms and clicking through to the website with decreasing
frequency. This migration directly threatens the AdSense-dependent
revenue model and explains the downward revenue trend visible in the
Monte Carlo historical data. The association rules analysis adds
nuance: when readers do arrive at the website, Music and Relationships
content drives the deepest cross-category engagement, suggesting that
the content editorial strategy is sound... it is the distribution
model, not the content itself, that requires transformation.

The second finding is a commercial retention crisis that is both
severe and recoverable. The Kaplan-Meier survival analysis shows that
70.1% of The Company's 107 advertiser clients have already churned, with
survival probability falling below 50% by 18 months. Yet the RFM
analysis simultaneously identifies 25 Champion clients who remain
highly active with an average of 18.7 campaigns each and average spend
of ₦8.7 million,  demonstrating that deep, loyal advertiser
relationships are achievable. The gap between Champions and the 21
At Risk clients who averaged 5.4 campaigns before going silent
represents a recoverable revenue opportunity. The CLV analysis
identifies Corporate clients as the most sustainable category with the
best retention profile, suggesting that business development focus
should shift toward corporate and brand partnerships rather than
relying so heavily on the music industry's volatile campaign cycle.

The third finding is that content sentiment and co-consumption data
point toward a coherent content strategy that the company has not yet
fully operationalised. Facebook's 56% positive sentiment and the
strong Music–Relationships–Celebrity Gist co-consumption cluster both
confirm that The Company's core content identity, celebrity drama,
relationship narratives, and entertainment reaction content, is
genuinely resonant with its audience. The LDA topic model confirms
five coherent content themes that cut across traditional category
labels, suggesting that a theme-based content calendar would be more
aligned with actual audience behaviour than a category-based one.

The single integrated recommendation is that The Company must execute a
simultaneous three-part transformation: migrate its revenue model from
website-AdSense-dependent to social-platform-native by building
recurring brand partnerships on Instagram and Facebook; implement an
advertiser retention protocol that triggers a personalised re-engagement
outreach to every new client within 30 days of their first campaign
to prevent single-campaign churn; and restructure its content calendar
around the five LDA themes with Music and Relationships content always
published together and Comedy content scaled up as the highest
per-session engagement driver in the portfolio.

---

# 11. Limitations and Further Work

This analysis carries several limitations that should be acknowledged
in interpreting its findings. The social media post-level datasets
cover only the period from May 2025 to April 2026 due to Meta Business
Suite and X Analytics export restrictions on historical data, limiting
the ability to detect long-term sentiment trends on social platforms.
A full three-year social media dataset would substantially strengthen
the temporal analysis. The association rules technique was constrained
by GA4's Path Exploration export limitations, which prevented
true transaction-level session basket analysis. The co-occurrence
matrix was therefore derived from aggregated page-level session data
rather than individual reader path sequences, which means the
association rules represent tendencies at the category level rather
than precise Apriori confidence and lift metrics. With BigQuery
integration enabled on the GA4 property, session-level path data
would allow proper Apriori analysis with formal support, confidence,
and lift statistics.

The Monte Carlo simulation assumes revenue streams follow normal
distributions. With a longer historical record.. ideally five or more
years, fitting more appropriate parametric distributions such as
log-normal for revenue streams and triangular distributions for costs
would produce more accurate tail-risk estimates. The LDA topic model
used k=5 topics selected based on interpretability rather than a
formal coherence score evaluation. A grid search over k values from
3 to 10 with perplexity and coherence scoring would provide a more
rigorous basis for topic number selection.

With more data and computing time, this analysis would benefit from
a classification model, logistic regression or random fores, trained
to predict advertiser churn before it occurs using early campaign
behaviour signals such as the gap between first and second campaign,
the platform mix of initial campaigns, and the spend trajectory from
campaign to campaign. Such a model would enable proactive rather than
reactive client retention and represents the most commercially
impactful analytical extension of this work.

---

# References

Adi, B. (2026). *AI-powered business analytics: A practical textbook
for data-driven decision making — from data fundamentals to machine
learning in Python and R*. Lagos Business School / markanalytics.online.
https://markanalytics.online

R Core Team. (2024). *R: A language and environment for statistical
computing* (Version 4.x). R Foundation for Statistical Computing.
https://www.R-project.org/

Allaire, J. J., Teague, C., Scheidegger, C., Xie, Y., & Dervieux, C.
(2022). *Quarto* (Version 1.x) [Computer software].
https://doi.org/10.5281/zenodo.5960048

Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.,
François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J.,
Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K.,
Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., … Yutani H.
(2019). Welcome to the tidyverse. *Journal of Open Source Software*,
*4*(43), 1686. https://doi.org/10.21105/joss.01686

Taylor, S. J., & Letham, B. (2018). Forecasting at scale.
*The American Statistician*, *72*(1), 37–45.
https://doi.org/10.1080/00031305.2017.1380080

Rinker, T. W. (2021). sentimentr: Calculate text polarity sentiment
(Version 2.9.0). https://github.com/trinker/sentimentr

Blei, D. M., Ng, A. Y., & Jordan, M. I. (2003). Latent Dirichlet
allocation. Journal of Machine Learning Research, 3, 993–1022.

Therneau, T., & Grambsch, P. (2000). Modeling survival data: Extending
the Cox model. Springer.

Kassambara, A., & Kosinski, M. (2021). survminer: Drawing survival
curves using ggplot2 (Version 0.4.9).
https://CRAN.R-project.org/package=survminer

Hahsler, M., Gruen, B., & Hornik, K. (2005). arules: A computational
environment for mining association rules and frequent item sets.
Journal of Statistical Software, 14(15), 1–25.
https://doi.org/10.18637/jss.v014.i15
---

# Appendix: AI Usage Statement

This analysis was completed with the assistance of Claude (Anthropic)
as an AI coding tool. The role of AI assistance was strictly limited
to the generation of R code chunks, code formatting, and syntax
optimisation across the five analytical techniques. Specifically,
Claude was used to generate boilerplate code structures for data
loading, visualisation scaffolding, and statistical modelling
functions.

All substantive analytical work was conducted independently by the
author, Tobi Oyetoro. This includes the collection and extraction of real
cross-platform data directly from the organisation's platform
backends — Google Analytics 4, Meta Business Suite, Instagram
Professional Dashboard, X Analytics, and internal financial and
campaign records. Data cleaning and preparation, including the
correction of formatting errors, standardisation of category labels,
handling of missing values, and restructuring of exports from
multiple platform formats into a unified analytical dataset, was
performed manually by the author, Tobi Oyetoro in Microsoft Excel prior to loading
into R.

The selection of analytical techniques, the business justification
for each technique relative to the organisation's specific operational
context, the interpretation of all model outputs and statistical
results, and the integrated recommendation were all products of
independent analytical judgement exercised by the author. The author
drew on domain knowledge of the organisation's content strategy,
revenue model, advertiser relationships, and audience behaviour
accumulated through direct professional involvement with the
organisation.

